\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-15 conclusion.tex
implemented all remaining changes for experimental, and conclusion section

\section{Conclusion}
\label{sec:conclusion}
This work introduced a new manufacturing approach for a soft manipulator and demonstrated its capabilities through autonomously grasping-and-placing a randomly positioned object.
To produce the complete soft manipulator used, an entirely soft gripper was designed and fabricated and then combined with a previously developed soft robotic arm.
It was then shown that a minimal strain and collision-free approach to an object of interest can be achieved by posing the grasp motion plan as a series of constrained nonlinear optimization problems.

@@

The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
\rkk{The ability to successfully and repeatedly perform object manipulation using a fully soft, multiple degree of freedom arm suggests} that despite their extreme compliance, soft robots are capable of \rkk{reliable and robust} object manipulation while simultaneously providing inherently safe interactions with the environment.
We \rkk{also} demonstrated the \rkk{manipulator's} ability to autonomously grasp an object, which leads to many potential applications \rkk{for full soft robotic manipulation}.
\rkk{In a manufacturing setting, this could resemble a soft robot stretched widely to pick up objects situated at various locations.}
In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
\rkk{To foster those assumptions, future work could investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
Integrating proprioceptive sensing \dr{\cite{homberg2015haptic}} within a multi-segment soft actuator will further improve the use of these manipulators in occluded environments.}
%The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.

>>>>

\section{Conclusion}
\label{sec:conclusion}
This work describes a planar soft manipulator capable of pick-and-place operations under high uncertainty in the position and shape of the object. 
%introduced a new manufacturing approach for a soft manipulator and demonstrated its capabilities through autonomously grasping-and-placing a randomly positioned object.
%To produce the complete soft manipulator used, an entirely 
A soft gripper was designed, fabricated, and combined with a previously developed soft robotic arm.
It was then shown that a minimal strain and collision-free approach to an object of interest can be achieved by posing the grasp motion plan as a series of constrained nonlinear optimization problems.

@@

The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
\rkk{The ability to successfully and repeatedly perform object manipulation using a fully soft, multiple degree of freedom arm suggests} that despite their extreme compliance, soft robots are capable of \rkk{reliable and robust} object manipulation while simultaneously providing inherently safe interactions with the environment.
We \rkk{also} demonstrated the \rkk{manipulator's} ability to autonomously grasp an object, which leads to many potential applications \rkk{for full soft robotic manipulation}.
\rkk{In a manufacturing setting, this could resemble a soft robot stretched widely to pick up objects situated at various locations.}
In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
%Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
\rkk{Future work will investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
Integrating proprioceptive sensing within a multi-segment soft actuator will further improve the use of these manipulators in occluded environments.}
%The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.

### 2015-10-15 experimental_results.tex
implemented all remaining changes for experimental, and conclusion section

\section{Experimental Results}
\label{sec:experimental_results}
In the following section summarizes the results from experiments with the soft manipulator. We discuss the grasping of delicate objects and cylindrical objects as well as the repeatability and success rate of the autonomous system.

\subsection{Aggregate System}
\label{sec:aggregate_system}
The aggregate \dr{soft manipulation} system is shown in Figure~\ref{fig:sys_overview}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
As our localization system, the OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable and consistent hardware experiments without the need for recalibration.

@@

\subsection{Grasping Delicate Objects}
\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can be contiuously actuated in a pressure range of 0-60\unit{kPa} and create blocking forces in the range of 0-2\unit{N}. This fine actuation range and the fact that soft manipulators easily conform to shapes implies that grasping delicate objects should be possible.}
The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
Figure~\ref{fig:egg_approach_sequence} shows \rkk{for example} how the manipulator approaches and grasps an egg.
Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.

@@

\subsection{Repeated Grasp Experiments}
We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
The results of all the trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the other trials, the grasp and return was successfully performed, but a small overshoot over the final bin location at the end of the return caused the arm to drop off the table, which could have been avoided if the table would have not been too small towards the right.
This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.

\subsection{Experimental Insights and Limitations}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper. A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

>>>>

\section{Experimental Results}
\label{sec:experimental_results}
%In the following section summarizes the results from experiments with the soft manipulator. 
We now discuss the grasping of objects as well as the repeatability and success rate of the autonomous system.

\subsection{Aggregate System}
\label{sec:aggregate_system}
The aggregate \dr{soft manipulation} system is shown in Figure~\ref{fig:sys_overview}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.

@@

%\subsection{Grasping Delicate Objects}
%\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can be contiuously actuated in a pressure range of 0-60\unit{kPa} and create blocking forces in the range of 0-2\unit{N}. This fine actuation range and the fact that soft manipulators easily conform to shapes implies that grasping delicate objects should be possible.}
%The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
%Figure~\ref{fig:egg_approach_sequence} shows \rkk{for example} how the manipulator approaches and grasps an egg.
%Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
%Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.

@@

\subsection{Repeated Grasp Experiments}
We performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
%To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
%The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
%It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
%In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
%The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the trials shown in Figure~\ref{fig:allTestsOverlaid}, the grasp and return was successfully performed, but an overshoot over the final bin location caused the arm to drop off the relatively small table.
%, which could have been avoided if the table would have not been too small towards the right.
%This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.

\subsection{Experimental Insights and Limitations}
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
%Most of the payload capability is already used up by the attached gripper itself.
%A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
%The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
%\rkk{The gripper presented did not only pick up round objects, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
%Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment. 
%, around half the length of the gripper. 
%A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
%\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}

\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}
